Follow-up Samples

### 2017-09-13 submission/manuscript_R2.tex

All models included only OTU data obtained from 16S rRNA sequencing and
were processed and cleaned using the R package caret (v6.0.76).
Optimization of the mtry hyper-parameter involved making 100 different
80/20 (train/test) splits of the data where the same proportion was
present within both the whole data set and the 80/20 split. For each of
the different splits, 20 repeated 10-fold cross validation was performed
on the 80\% component to optimize the mtry hyper-parameter by maximizing
the AUC (Area Under the Curve of the Receiver Operator Characteristic).
The resulting model was then tested on the hold out data obtained from
the 20\% component. For adenoma pre versus post-treatment models the
optimized mtrys were 2 (n = 42), 42 (n = 26), and 914 (n = 32) for
adenoma. For advanced adenoma the mtrys were 2 (n = 26), 52 (n = 14),
and 1353 (n = 60). For carcinoma the mtrys were 2 (n = 36), 41 (n = 54),
and 863 (n = 10). For the normal versus diagnosis models the optimized
mtrys were (n = NA), (n = NA), and (n = NA) for adenoma. For advanced
adenoma (n = NA), (n = NA), and (n = NA). For carcinoma (n = NA), (n =
NA), and (n = NA). The hyper-parameter, mtry, defines the number of
variables to investigate at each split before a new division of the data
was created with the Random Forest model (33).

>>>>

All models included only OTU data obtained from 16S rRNA sequencing and
were processed and cleaned using the R package caret (v6.0.76).
Optimization of the mtry hyper-parameter involved making 100 different
80/20 (train/test) splits of the data where the same proportion was
present within both the whole data set and the 80/20 split. For each of
the different splits, 20 repeated 10-fold cross validation was performed
on the 80\% component to optimize the mtry hyper-parameter by maximizing
the AUC (Area Under the Curve of the Receiver Operator Characteristic).
The resulting model was then tested on the hold out data obtained from
the 20\% component. For adenoma pre versus post-treatment models the
optimized mtrys were 2 (n = 42), 42 (n = 26), and 914 (n = 32) for
adenoma. For advanced adenoma the mtrys were 2 (n = 26), 52 (n = 14),
and 1353 (n = 60). For carcinoma the mtrys were 2 (n = 36), 41 (n = 54),
and 863 (n = 10). For the normal versus diagnosis models the optimized
mtrys were 2 (n = 16), 37 (n = 44), and 707 (n = 40) for adenoma. For
advanced adenoma 2 (n = 33), 37 (n = 50), and 696 (n = 17). For
carcinoma 36 (n = 96) and 649 (n = 4). The hyper-parameter, mtry,
defines the number of variables to investigate at each split before a
new division of the data was created with the Random Forest model (33).
